Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/casestudy.tex
Consistency

Note that, by TypeScript's structural typing
\cite{TypeScriptSpec}, replacing
\texttt{handleP2Move} on \cref{lineupdate} with a recursive
occurrence of \texttt{handleP1Move} would be
type-correct --- this allows for better code reuse as opposed to
defining
additional abstractions to work around the limitations of nominal
typing in
\cite{Hybrid2016}.
There is also full type erasure when transpiling to JavaScript to
run the
server code, so the types defined in TypeScript will not appear in the
JavaScript after typechecking.
This means state space explosion is not a runtime consideration.

>>>>

Note that, by TypeScript's structural typing
\cite{TypeScriptSpec}, replacing
\texttt{handleP2Move} on \cref{lineupdate} with a recursive
occurrence of \texttt{handleP1Move} would be
type-correct --- this allows for better code reuse as opposed to
defining
additional abstractions to work around the limitations of nominal
typing in
\cite{Hybrid2016}.
There is also full type erasure when transpiling to JavaScript to
run the
server code, so the types defined in TypeScript will not appear in the
JavaScript after type-checking.
This means state space explosion is not a runtime consideration.
